%-------------------------
% Resume in Latex
% Author : Dhruv Chaudhary (Core – Balanced Software & Hardware Focus, Impact-Driven Final)
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\resumeItem}[1]{\item\small{{#1 \vspace{-2pt}}}}
\newcommand{\resumeSubheading}[4]{\vspace{-2pt}\item
  \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
    \textbf{#1} & #2 \\
    \textit{\small#3} & \textit{\small #4} \\
  \end{tabular*}\vspace{-7pt}}
\newcommand{\resumeProjectHeading}[2]{\item
  \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
    \small#1 & #2 \\
  \end{tabular*}\vspace{-7pt}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=0.15in]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}

%-------------------------------------------
\begin{document}

%-----------HEADER-----------
\begin{center}
    \textbf{\Huge \scshape Dhruv Chaudhary} \vspace{4pt} \\[-2pt] 
    \footnotesize
    425-591-6187 $|$
    \href{mailto:dhruv.chaudhary@hotmail.com}{dhruv.chaudhary@hotmail.com} $|$
    \href{https://linkedin.com/in/DhruvChaudhary1215}{linkedin.com/in/DhruvChaudhary1215} $|$
    \href{https://github.com/Duhuhruv}{github.com/Duhuhruv} $|$
    U.S. Citizen
\end{center}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Purdue University}{West Lafayette, IN}
      {Bachelor of Science in Computer Engineering}{Aug 2021 -- May 2025}
  \begin{itemize}[leftmargin=0.05in, label={}]
    \small{\item{
     \textbf{Relevant Coursework:} Data Structures and Algorithms, Operating Systems, Communication Networks, AI/ML, Microprocessor Systems, C++ OOP, Python for Data Science, Digital Systems Design, Signals and Systems.\\
    }}
 \end{itemize}
  \resumeSubHeadingListEnd

%-----------EMPLOYMENT-----------
\section{Employment}
  \resumeSubHeadingListStart
    \resumeSubheading
      {SeaTec Consulting}{Bellevue, WA}
      {Aerospace and Defense Intern I \& II}{May 2022 -- Aug 2023}
      \resumeItemListStart
        \resumeItem{Saved over \textbf{10,000 labor hours across the program} by automating Boeing’s IP documentation review with a Python/VBA pipeline that processed 18K+ technical files, reducing the contract-allocated 6-hour review per document to under 1 minute.}
        \resumeItem{Created automation scripts in Access and Excel to streamline configuration management workflows and error tracking for aircraft system documentation.}
        \resumeItem{Streamlined airspace data-sharing documentation for NASA’s Urban Air Mobility Challenge by consolidating cross-team research and verification workflows.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------ENGINEERING EXPERIENCE-----------
\section{Engineering Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Senior Design: Object Detection Drone}{West Lafayette, IN}
      {Communications and Embedded Systems Lead}{Jan 2025 -- May 2025}
      \resumeItemListStart
        \resumeItem{Achieved stable 3 km Sub-GHz image transmission at 1 Mbps by designing a custom packet protocol and embedded C firmware on the TI CC1312R.}
        \resumeItem{Integrated Python-based compression and reliability testing to improve throughput and minimize data loss.}
        \resumeItem{Led communications development, coordinating RF integration and firmware across a four-person team.}
      \resumeItemListEnd

    \resumeSubheading
      {Engineering Projects in Community Service (EPICS)}{West Lafayette, IN}
      {Project Partner Liaison}{Aug 2021 -- May 2022}
      \resumeItemListStart
        \resumeItem{Translated client therapy goals into engineering deliverables by leading collaboration with a hippotherapy organization serving children with special needs.}
        \resumeItem{Developed servo-controlled assistive robotics with embedded C and sensor-actuator interfacing, ensuring reliability.}
        \resumeItem{Presented functional prototypes to 500+ attendees at Purdue Space Day, demonstrating real-time motion control.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeProjectHeading
      {\textbf{NPM Package Rater / NPM Clone} $|$ \emph{TypeScript, AWS Services, GitHub Actions}}{Aug 2024 -- Jan 2025}
      \resumeItemListStart
        \resumeItem{Migrated package evaluation logic to \textbf{AWS Lambda}, refactoring modules for execution with API Gateway, S3, and DynamoDB integration.}
        \resumeItem{Implemented and maintained \textbf{CI/CD pipelines} using GitHub Actions to automate Lambda deployments and minimize manual configuration.}
        \resumeItem{Developed structured logging with \textbf{Winston} and integrated \textbf{Jest} testing for functionality and accessibility validation.}
        \resumeItem{Collaborated on modular system design linking AWS services, improving reliability and scalability of the package analysis prototype.}
      \resumeItemListEnd
    \resumeProjectHeading
      {\textbf{Data-Regularized Q-Learning in Snake} $|$ \emph{PyTorch, Reinforcement Learning}}{Jan 2025 -- May 2025}
      \resumeItemListStart
        \resumeItem{Increased model stability and convergence speed by implementing and benchmarking multiple RL algorithms in a custom Snake environment.}
        \resumeItem{Demonstrated 25\% faster learning and higher score stability with DrQ versus baselines, publishing results in an ICML-style paper and live demo.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages:} C, C++, Python, TypeScript, Java, MATLAB, RISC-V Assembly, LaTeX \\
     \textbf{Software Engineering:} Distributed Systems, REST APIs, CI/CD, AWS, Testing (Jest), Logging (Winston) \\
     \textbf{Tools:} Git, Node.js, Linux, VS Code, IntelliJ, RESTler, GDB, Valgrind, Agile Development \\
     \textbf{AI/ML:} PyTorch, Model Training, Data Augmentation, Reinforcement Learning \\
     \textbf{Awards:} Purdue Dean’s List (Dec 2021), Perfect Volunteer Attendance – Outdoors for All / Special Olympics (2020) \\
    }}
 \end{itemize}

\end{document}
